Supplementary Materials to ``Addressing selection bias and measurement error in COVID-19 case count data using auxiliary information''

### 2022-09-20 write-up/covid-supplement-writeup.tex
Update covid-supplement-writeup.tex
Updated papers - almost there
supplementary materials, final pass

\title[Statistical paradoxes in coronavirus case-counts]{Supplementary Materials to ``Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic''} %

@@

\begin{abstract}
This is the supplementary materials to the manuscript titled ``Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic.''  Section~\ref{app:imperfect} derives the statistical decompositions for the measurement-error corrected estimator and provides the connection to model-based estimators. Sections~\ref{app:ipwderivation} and~\ref{app:DRderivation} derives the statistical decomposition for the inverse-probability weighted and doubly robust estimators respectively.
Section~\ref{app:asympderivations} gives the proof for the asymptotics of the inverse-probability weighted estimator.  
Section~\ref{app:irls} outlines the iteratively re-weighted least squares algorithm.
Section~\ref{app:in_add_details} provides additional detals on the COVID-19 analysis of Indiana's case-count data.
Section~\ref{app:prior_modelbased} provides prior specifications for the SEIR model.
\end{abstract}

@@

Figure~\ref{fig:undercounting} is a plot of undercount based on the SEIR model.  We plot relative undercount on a cumulative basis since January due to the case counts reflecting active infections. Figure~\ref{fig:tv_air_sens} is a sensitivity analysis of the active infection rate under SEIR model with 10\% increase and decrease in the average IFR.  We see that the impact on the doubly robust estimates is minimal.

@@

Here we present estimates of the instantaneous reproductive number using the approach of~\cite{Cori20113} under the SEIR model from Section~\ref{section:r0-estimation}.  Let~$I_t$ denote the total infectiousness of infected individuals at time~$t$.  Then~$E[I_t] = R_t \sum_{s=1}^{t} I_{t-s} w_s$ where $w_{u}$ is the infectivity function.  Here, we follow~\cite{Cori20113} and choose a discretized shifted Gamma distribution with mean $7$ days and standard deviation $2$ days.  Then a moment-based estimator can be obtained by $\hat R_t = I_t / \sum_{s=1}^t I_{t-s} w_s$, which takes the form of the ratio estimators in Section~\ref{section:rates}.  Therefore, the bias can be readily obtained from the associated Taylor series decomposition, with the terms related to time~$t-1$ replaced by a weighted version.  Figure~\ref{fig:cori-bias} presents the bias.

>>>>

\title[Addressing selection bias and measurement error in COVID-19 case counts]{Supplementary Materials to ``Addressing selection bias and measurement error in COVID-19 case count data using auxiliary information''} %

@@

\begin{abstract}
This is the supplementary materials to the manuscript titled ``Addressing selection bias and measurement error in COVID-19 case count data using auxiliary information.''  Section~\ref{app:imperfect} derives the statistical decompositions for the measurement-error corrected estimator and provides the connection to model-based estimators. Sections~\ref{app:ipwderivation} and~\ref{app:DRderivation} derives the statistical decomposition for the inverse-probability weighted and doubly robust estimators respectively.
Section~\ref{app:asympderivations} gives the proof for the asymptotics of the inverse-probability weighted estimator.  
Section~\ref{app:irls} outlines the iteratively re-weighted least squares algorithm.
Section~\ref{app:in_add_details} provides additional detals on the COVID-19 analysis of Indiana's case-count data.
Section~\ref{app:prior_modelbased} provides prior specifications for the SEIR model.
\end{abstract}

@@

Figure~\ref{fig:undercounting} is a plot of undercount based on the SEIR model.  We plot relative undercount on a cumulative basis since January due to the case counts reflecting active infections. Figure~\ref{fig:tv_air_sens} is a sensitivity analysis of the active infection rate under SEIR model with 10\% increase and decrease in the average IFR.  We see that the impact on the doubly robust estimates is minimal.  A floor based on weekly case count divided by the Indian population size is also presented.

@@

Here we present estimates of the instantaneous reproductive number using the approach of~\cite{Cori20113} under the SEIR model from Section~\ref{section:r0-estimation}.  Let~$I_t$ denote the total infectiousness of infected individuals at time~$t$.  Then~$E[I_t] = R_t \sum_{s=1}^{t} I_{t-s} w_s$ where $w_{u}$ is the infectivity function.  Here, we follow~\cite{Cori20113} and choose a discretized shifted Gamma distribution with mean $7$ days and standard deviation $2$ days.  Then a moment-based estimator can be obtained by $\hat R_t = I_t / \sum_{s=1}^t I_{t-s} w_s$, which takes the form of the ratio estimators in Section~\ref{section:rates}.  Therefore, the bias can be readily obtained from the associated Taylor series decomposition, with the terms related to time~$t-1$ replaced by a weighted version.
% Figure~\ref{fig:cori-bias} presents the bias.
